\documentclass[10pt, a4paper]{article}

\usepackage[a4paper, top=1.8cm, bottom=1.8cm, left=2cm, right=2cm]{geometry}
\usepackage{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{lastpage}

% ── Colours ──────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{30, 100, 180}
\definecolor{muted}{RGB}{100, 100, 100}
\definecolor{rule}{RGB}{200, 210, 225}

% ── Hyperlinks ────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent,
  pdfauthor={Rasika Edirisinghe},
  pdftitle={Rasika Edirisinghe — CV}
}

% ── Section formatting ────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}
  [\color{rule}\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}

% ── No page numbering ─────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\small\color{muted}Page \thepage\ of \pageref{LastPage}}

% ── List settings ────────────────────────────────────────────────────────────
\setlist[itemize]{leftmargin=1.5em, itemsep=1pt, topsep=2pt, parsep=0pt}

% ── Custom commands ───────────────────────────────────────────────────────────
\newcommand{\cventry}[4]{%
  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{#1} & \textcolor{muted}{\small #2} \\
    \textit{\textcolor{accent}{\small #3}} & \textcolor{muted}{\small #4}
  \end{tabularx}%
  \vspace{2pt}%
}

\newcommand{\cventryshort}[3]{%
  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{#1} & \textcolor{muted}{\small #2} \\
    \textit{\textcolor{accent}{\small #3}} &
  \end{tabularx}%
  \vspace{2pt}%
}

\newcommand{\tagsline}[1]{%
  \vspace{2pt}%
  \noindent\textcolor{muted}{\small \textit{Skills: #1}}%
  \vspace{4pt}%
}

% ─────────────────────────────────────────────────────────────────────────────

\begin{document}

% ── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Rasika Edirisinghe}\\[4pt]
  {\color{accent}\large Marie Curie Early Stage Researcher \textperiodcentered\ University College Cork, Ireland}\\[6pt]
  \small
  \href{mailto:rasikahendrix@gmail.com}{rasikahendrix@gmail.com} \textperiodcentered\
  \href{mailto:rasika.edirisinghe@ucc.ie}{rasika.edirisinghe@ucc.ie} \textperiodcentered\
  +353 87 266 6627\\
  \href{https://mrHendrixSL.github.io}{mrHendrixSL.github.io} \textperiodcentered\
  \href{https://www.linkedin.com/in/rasikaedirisinghe/}{linkedin.com/in/rasikaedirisinghe} \textperiodcentered\
  \href{https://github.com/mrHendrixSL/}{github.com/mrHendrixSL}\\
  \href{https://orcid.org/0009-0008-4673-0259}{orcid.org/0009-0008-4673-0259} \textperiodcentered\
  \href{https://scholar.google.com/citations?user=o_7ZjgMAAAAJ}{Google Scholar}
\end{center}

\vspace{4pt}

% ── Summary ───────────────────────────────────────────────────────────────────
\section{Summary}

AI researcher specialising in Natural Language Processing, Machine Learning, and Transformers, with a strong foundation in applied data visualization. Currently pursuing a fully funded PhD in Computer Science at University College Cork under the CASCADE Horizon Europe MSCA programme, developing LLM-powered text reuse detection systems for diachronic corpora and low-resource textual domains. Over four years of cross-functional industry experience building cloud-based BI tools and automation pipelines. Committed to delivering explainable, human-centered AI solutions for language and data-intensive environments.

% ── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\cventry{PhD in Computer Science (Reading)}{Sep 2024 -- Sep 2027 (expected)}{University College Cork, Ireland}{CASCADE Horizon Europe MSCA}
\textit{Thesis: Language Modelling and Visualization for Parallel Text Analysis}
\begin{itemize}
  \item Designing advanced text reuse detection systems for diachronic corpora and low-resource textual domains using LLMs and interactive visual analytics.
  \item Addressing orthographic variation, semantic drift, and context-dependent alignment across time and textual use cases.
\end{itemize}
\vspace{4pt}

\cventry{M.Sc. Business Analytics \textnormal{--- Distinction}}{Sep 2021 -- Sep 2023}{Robert Gordon University, Aberdeen, UK}{}
\textit{Thesis: Twitter Sentiment Reason Mining Framework to Identify Major Problems in US Healthcare Industry} (Grade: A)\\
Key modules: Data Management (A) \textperiodcentered\ Web Mining (A) \textperiodcentered\ BI Tools \& Applications (A) \textperiodcentered\ Intro to Big Data \& Data Science (A)
\vspace{4pt}

\cventry{B.Sc. (Hons) Business Information Systems}{Nov 2016 -- Oct 2018}{Cardiff Metropolitan University, Cardiff, UK}{}
\textit{Thesis: Computer-Aided Diagnosis System for Lung Cancer Detection} (Java-based CADe system)
\vspace{4pt}

\cventry{BTEC Higher National Diploma, Software Development}{May 2014 -- May 2016}{Pearson Edexcel, UK}{}
OOP \textperiodcentered\ Data Structures \& Algorithms \textperiodcentered\ Networking Technologies \textperiodcentered\ Web Applications \textperiodcentered\ Database Development

% ── Academic Experience ───────────────────────────────────────────────────────
\section{Academic Experience}

\cventry{Teaching Assistant \& Co-Lecturer --- Data Visualization for Machine Learning}{2025/26}{University College Cork}{CS3205 / CS6426}
\begin{itemize}
  \item Revamped lecture and lab materials for the 2025/26 cohort.
  \item Delivered lectures and hands-on Python lab sessions.
  \item Created all lecture slide decks for 2026 delivery.
  \item Assessed and graded student assignments and examinations.
\end{itemize}
\tagsline{Data Visualization, Machine Learning, Python, University Teaching, Assessment}

\cventry{Visiting Lecturer}{Aug 2023 -- Sep 2024}{University of Ruhuna, Dept.\ of Electrical \& Information Engineering}{Galle, Sri Lanka}
\begin{itemize}
  \item \textbf{Introduction to Data Visualization with Power BI} --- DAX, dashboards, Gestalt principles, color theory.
  \item \textbf{Excel for Data Science} --- PivotTables, time-series, statistical analysis, Solver.
  \item \textbf{Data Preprocessing \& Cleaning} --- missing data, outlier detection, encoding.
  \item \textbf{Data Splitting \& Cross Validation} --- overfitting, metrics, confusion matrix.
\end{itemize}
\tagsline{Data Science Teaching, Power BI, Excel Analytics, ML Foundations}

\cventry{Visiting Lecturer}{Aug 2023 -- Sep 2024}{Sri Lanka Telecom Training Centre, Sri Lanka Telecom PLC}{Welisara, Sri Lanka}
\begin{itemize}
  \item \textbf{Fundamentals of AI \& Intelligent Systems} (Pearson BTEC K/618/5660) --- AI types, NLP, conversational AI, ethics.
  \item \textbf{Big Data \& Visualization} (J/618/6251) --- Python, Jupyter, Power BI, DAX, data governance.
  \item \textbf{Business Intelligence} (M/615/1641) --- BI systems, OLAP, descriptive \& predictive analytics.
\end{itemize}
\tagsline{AI Education, Big Data, Business Intelligence, Higher Education Teaching}

% ── Industry Experience ───────────────────────────────────────────────────────
\section{Industry Experience}

\cventry{Data Analyst}{May 2023 -- Sep 2024}{EFL Global}{Colombo, Sri Lanka (Hybrid)}
\begin{itemize}
  \item Automated global finance reporting across 39 countries \& 70+ offices (Python, VBA, Advanced Excel).
  \item Modelled and maintained Azure Databricks backend for automated MIS, AR \& AP reporting.
  \item Built Power BI \& Tableau dashboards; implemented workflows via Power Automate \& Logic Apps.
  \item Managed Azure Analysis Services, Data Lakes, Blob Storage, and Synapse Analytics.
\end{itemize}
\tagsline{Python, Azure Databricks, Power BI, Tableau, Power Automate, Azure Synapse}

\cventry{Implementation Engineer}{Nov 2022 -- May 2023}{Affno Asia Pacific}{Colombo, Sri Lanka}
\begin{itemize}
  \item Designed and deployed BI solutions for supply chain analytics.
  \item Acted as Technical Business Analyst, translating business needs into system designs.
  \item Provided training and support to clients in reporting and analytics.
  \item Worked with Amazon EC2 \& MongoDB Atlas for cloud-based solutions.
\end{itemize}
\tagsline{Business Intelligence, Supply Chain Analytics, MongoDB, Business Analysis}

\cventry{Operations Analyst}{Sep 2019 -- Nov 2022}{SYNERGEN Health}{Colombo, Sri Lanka}
\begin{itemize}
  \item Managed Qlik-Sense cloud-based RCM BI platform (Doctrix) for real-time KPI \& SLA monitoring.
  \item Led process training for multiple clients in Revenue Cycle Management.
  \item Implemented Python \& VBA automation for financial reporting and data integrity.
  \item Maintained Amazon DynamoDB \& Kinesis Data Streams for real-time analytics.
\end{itemize}
\tagsline{Healthcare BI, QlikSense, Revenue Cycle Analytics, Python, VBA}

\cventry{Associate Operations Analyst \textnormal{(Intern)}}{Mar 2019 -- Sep 2019}{SYNERGEN Health}{Colombo, Sri Lanka}
Client reporting, process monitoring, data sanity checks, and trade support.

\cventry{Business Analyst \textnormal{(Intern)}}{Sep 2018 -- Mar 2019}{Global System Solutions}{Colombo, Sri Lanka}
Requirement gathering, use case development, reporting specification, pre-sales support.

% ── Publications ──────────────────────────────────────────────────────────────
\section{Publications \& Research Output}

\textbf{Rewriting Tradition: Quantifying Change in Lady Gregory's Irish Legends}\\
Rachel McCarthy, Rasika Edirisinghe, James O'Sullivan, Clíona Ó Gallchoir, Rosane Minghim, Órla Murphy\\
\textit{DH2025: Alliance of Digital Humanities Organizations} \textperiodcentered\ Lisbon, Portugal \textperiodcentered\ Jul 2025 \textperiodcentered\ \textcolor{accent}{Abstract Accepted}
\vspace{6pt}

\textbf{Sentiment Reason Mining Framework for Analyzing Twitter Discourse on Critical Issues in US Healthcare Industry}\\
R. Edirisinghe, P. P. G. Dinesh Asanka\\
\textit{International Conference on Smart Computing and Systems Engineering 2023} \textperiodcentered\ Aug 2023\\
\href{https://ieeexplore.ieee.org/document/10215010/}{ieeexplore.ieee.org/document/10215010}

\subsection*{\normalsize\color{muted}Work in Progress}
\vspace{-4pt}
\begin{itemize}
  \item \textbf{Text Reuse Detection with Large Language Models} --- PhD research, UCC (CASCADE MSCA)
  \item \textbf{Interactive Visualization for NLP Interpretability} --- open-source tool, PhD research, UCC
  \item \textbf{Parsing Hiberno-English Dictionary Entries: A Hybrid Rule-Based and LLM Approach} --- under preparation; presentation accepted at \textit{Digital Humanities Congress 2026}, University of Sheffield, Sep 2--3 2026
  \item \textbf{Trust \& Agency in Agentic Cyber-Physical Systems} --- Nimbus Research Centre, inTrusted project
\end{itemize}

% ── Presentations & Contributions ─────────────────────────────────────────────
\section{Presentations \& Academic Contributions}

\textbf{Beyond Translation: Rethinking `Parallel Text' Across Disciplines}\\
\textit{UCC Digital Humanities Colloquium} \textperiodcentered\ University College Cork \textperiodcentered\ 1 October 2025

\textbf{Language Modelling and Visualization for Parallel Text}\\
\textit{CACSSS PhD Lightning Talks} \textperiodcentered\ University College Cork \textperiodcentered\ 4 April 2025

\textbf{Sentiment Reason Mining Framework \ldots\ (paper presentation)}\\
\textit{International Conference on Smart Computing and Systems Engineering 2023} \textperiodcentered\ June 2023
\vspace{4pt}

\textbf{Peer Reviewer} --- 8th International Research Conference on Smart Computing and Systems Engineering (SCSE 2025), Feb 2025\\
\textbf{Evaluator} --- System Development Project Poster Presentation, University of Kelaniya, Oct 2023\\
\textbf{Curriculum Reviewer} --- Foundation to Data Science, University of Ruhuna, Aug 2023

% ── Skills ────────────────────────────────────────────────────────────────────
\section{Skills \& Technologies}

\begin{tabularx}{\textwidth}{@{}>{\bfseries}p{3.8cm}X@{}}
Languages       & Python, SQL, Java, JavaScript, C\#, R, VBA \\[2pt]
NLP \& LLMs     & HuggingFace Transformers, spaCy, Gensim, NLTK, OpenAI API, Prodigy \\[2pt]
ML / DL         & PyTorch, TensorFlow, Keras, scikit-learn, XGBoost \\[2pt]
Visualization   & Power BI, Tableau, QlikView/Sense, Plotly, Matplotlib, Seaborn, DAX \\[2pt]
Cloud           & Azure (Databricks, Synapse, Blob, Logic Apps), AWS (EC2, DynamoDB, Kinesis), MongoDB Atlas \\[2pt]
Databases       & MySQL, MongoDB, Amazon DynamoDB \\[2pt]
Dev Tools       & Git, Jupyter, Weka, Orange, HTML/CSS, ASP.NET, Power Automate, Bash \\[2pt]
Soft Skills     & Technical communication with non-technical audiences, tutoring \& mentoring, business process design, collaborative team player \\
\end{tabularx}

% ── Current Secondment ────────────────────────────────────────────────────────
\section{Current Secondment}

\cventry{Research Secondment --- inTrusted Project}{Apr 2026 -- Jul 2026}{Nimbus Research Centre}{Cork, Ireland}
Working with Tharindu Ranathunga on the \href{https://nimbuscentre.ie/project/intrusted/}{inTrusted} project --- exploring trust frameworks for agentic cyber-physical systems, and the gap between human intentionality, AI interpretation, and real-world actions.

\end{document}
